\documentclass{article}
\usepackage{url}
\usepackage[utf8]{inputenc}
\usepackage{xepersian}
\settextfont[Scale=1.2]{Nazli}
\setlatintextfont[Scale=1.1]{Times New Roman}
\newcommand{\site}[1]{\texttt{#1}} % and \newcommand{\CTAN} % {http://ctan.org} in the preamble and \site{\CTAN} in the body text
%\hyphenation{acro-nym}
%\hyphenation{ac-ro-nym ac-ro-nym-ic a-cro-nym-i-cal-ly}
%\hyphenation{indivisible}
%\usepackage{microtype}
%\usepackage[noligatures]{microtype}
%\usepackage{parskip}
\begin{document}
\begin{latin}
\site{www.tug.org}\\
\site[ftp]{www.gnu.org}\\[2cm]
\url{www.yoosofan.github.io}
\parbox{1.5cm}{My name is Ahmad Yoosofan. }
\parbox{1.8cm}{\LaTeX  is an intersting tool for typing.} 
\parbox{1.6cm}{Learning \LaTeX is not easy.} 
This is not a parbox.1
\\ \par\noindent
\url{www.yoosofan.kashanu.ac.ir} \\
test
\quad\parbox[b]{1.8cm}{My name is Ahmad Yoosofan. }
\quad\parbox{1.8cm}{\LaTeX  is an intersting tool for typing.} 
\quad\parbox[t]{1.6cm}{Learning \LaTeX is not easy.} \\
This is a parbox with 3 centimeter width.
\\ \par\noindent
%c t b s
Text line\footnote{This is footnote in this page.}
\quad\parbox[b]{1.8cm}{this parbox is aligned at its bottom line}
\quad\parbox{1.5cm}{center-aligned parbox}
\quad\parbox[t]{2cm}{another parbox aligned at its top line}
\par\noindent
\begin{minipage}{3cm}
My name is Ahmad Yoosofan, \LaTeX is an interesting tool for typing. Learning \LaTeX is 
difficult\footnote{minipage can be used for long box.}. Simple text.
\end{minipage}\\
\mbox{3cm}{indivisible.\\My name is Ahmad Yoosofan, \LaTeX is an interesting tool for typing. Learning \LaTeX is difficult\footnote{minipage can be used for long box.}. Simple text.
} \par\noindent
ff fi flffiffl -- ---  \\
f\/f f\/i f\/l f\/f\/i f\/f\/l -\/- -\/-\/- \\
Here are three dots... compare them to the ellipsis\ldots \\
\'{a} \`{o} \^{a}  \"{u} \~{n}  \={o} \.{a} \v{e} \H{e} \t{aa} \c{b} \d{n}  \b{i} \~{m} \t{a} \t{bb} \\
\\
\end{latin}
سلام
\\
\begin{latin}
Não compreendo. Há aqui alguém que fale inglês?
Comment çava? Où se trouve l'aéroport? \\
\quad\parbox{2cm}{\raggedright
My name is Ahmad Yoosofan. I am trying to learn \LaTeX.  This parbox is not justified by using raggedright.
}
\quad\parbox{2cm}{\raggedleft
My name is Ahmad Yoosofan. I am trying to learn \LaTeX.  This parbox is not justified by using raggedleft.
}  \\
{\centering
\huge\bfseries Centered text \\
\Large\normalfont written by me \\
\normalsize\today
}
\par \noindent This is the beginning of a poem
by Edgar Allan Poe:
\begin{center}
\emph{Annabel Lee}
\end{center}
\begin{center}
It was many and many a year ago,\\
In a kingdom by the sea,\\
That a maiden there lived whom you may know\\
By the name of Annabel Lee
\end{center}
The complete poem can be read on
\url{http://www.online-literature.com/poe/576/}.\\
Which of the following designates the end of a paragraph.
\end{latin}
\end{document}
